\documentclass{article}

\title{Visualizing the TDD Cycle}
\author{Michael Hilton \and Caius Brindescu \and Mihai Codoban}

\begin{document}

\maketitle

\section{Software Artifact}

We plan to use data that we have collected from software being developed in order to visualize the software development process.  

\section{Why is this important?}
Test Driven Development (TDD) is a well defined software development process which consists of writing tests, writing code, and then refactoring.
While this process is fairly clear, there is no way to compare the theoretical process to how any develop actually is performing TDD.   

We would like to study how TDD is actually implemented in practice.
The first step to be able to perform this research is to record and analyze the process as it happens.
We have begun to develop the software to record this process, and have found that this software produces a very large quantity of data.
We want to develop visualizations to enable us to make more sense of this large volume of data.  

Without this research, developers can’t record and analyze themselves as they practice TDD.
Managers do not know if their employees are following TDD closely or at all.
Researchers do not have the required data to begin analyzing the practice of TDD.

\section{Target Audience}

The target audience for this visualization is anyone who wants to know about how the software development process happened.
We anticipate this would mostly be developers analyzing their own development cycle, researchers analyzing development cycles, and managers analyzing the development cycle of those that they are managing.  

\section{Questions that our audience might ask from the data}

\begin{itemize}
\item Developers
\begin{enumerate}
\item Is my TDD workflow consistent?
\item What does my TDD workflow look like?
\item How does my TDD workflow compare to others’?
\item Is my TDD workflow considered healthy?
\item Is my TDD workflow improving or worsening?
\end{enumerate}

\item Researchers
\begin{enumerate}
\item How does a practical TDD workflow look like?
\item How does practical TDD differ from theoretical TDD?
\item Are there correlations between TDD workflow characteristics and other software development phenomena?
\end{enumerate}

\item Managers
\begin{enumerate}
\item How is TDD affecting the project?
\item Who are the best TDD performers?
\item How consistent are my developers in using TDD?
\end{enumerate}
\end{itemize}

\section{The Data}

The data consists of a stream of development events recorded in an IDE:
\begin{itemize}
\item Text edits (each key stroke with origin (user, paste, undo, redo) )
\item Copy
\item Refactorings invoked 
\item Program runs
\item Test runs
\item Resource change events (add, delete, save, refresh)
\end{itemize}

The event stream is persisted in JSON.
Using this data we can infer high level TDD phases such as when the developer was writing tests, writing code to make the tests pass or when refactoring.

\section{How will we get the data?}

We have this data as part of the research we are doing.
We plan on eventually using automated data mining for this project, but we might need to mark up the data by hand for this class.  

\section{Initial design Thoughts}

We plan to have 3 visualizations depending on the scope of change:
\begin{itemize}
\item TDD flow visualization: the user can observe the sequence of TDD phases
\item TDD phase visualization: the user can observe a single TDD phase in detail
\item Code skimming: the user can observe code changes pertaining to different aspects of a TDD phase (code edits in tests, code edits in refactorings, etc)
\end{itemize}

\end{document}